\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

\IEEEPARstart{S}{tress} can have detrimental effects on the human body, ranging from depression, anxiety and social withdrawal to sleep deprivation and obesity. Stress has a direct impact on the cardiovascular system and therefore influences the heart beat. There are many ways to measure these cardiovascular signals and to track the level of stress. Traditional methods include contact-based sensors, such as chest straps or pulse oximeters. These are very precise but on the other hand, impractical during daily use. To solve this issue, remote Photoplethysmography (rPPG) proposes a solutions to these limitations. This technology uses standard video cameras to monitor the skin color and filter for subtle skil-color variations that are caused by flowing blood. With the information the heart rate can be calculated \cite{verkruysse2008remote}. These measurements can be directly reported back to the user using biofeedback. Biofeedback describes a therapeutic concept in which a user receives real-time information about their physiological processes, such as respiration or heart rate. This data is typically made accessible through an output device, such as a visual display. Alternatively, the information can be translated into different forms, such as auditory signals. The primary goal of biofeedback is to make these biological processes perceptible, enabling the user to gain conscious awareness and control over
functions that were previously automatic \cite{giggins2013biofeedback}.

The objective of this paper is to evaluate such a camera-based stress tracking system combined with musical biofeedback. The goal is to analyze if such a system can be used to lower stress levels and regulate consciousness. In the second chapter theoretical foundations such as stress, consciousness and rPPG techniques are investigated. In the third chapter, case studies will be analyzed. The fourth chapter evaluates whether such a system is theoretically feasible.

% According to MCEwen (2017), the brain is the central organ that perceives stress
% and handles accordingly in the body. It has a direct impact on the cardiovascular system and thereforce influences the heart rate \cite{mcewen2017neurobiology}.  Consequently, it is important to monitor these systems to detect whether a person is experiencing high levels of stress

% There are many different ways to measure these cardiovascular signals. Traditional methods include contact-based sensors, such as chest straps or pulse oximeters. These are very precise but on the other hand impractical during daily use. To solve this issue, remote Photoplethysmography (rPPG) proposes a solutions to these limitations. This technology uses standard video cameras to monitor the skin color and filter for subtle skil-color variations that are caused by flowing blood. With the information the heart rate can be calculated \cite{verkruysse2008remote}.