\section{Discussion}

In this chapter, the final argumentation for the closed-loop system is presented. It discusses whether a camera-based approach using rPPG combined with musical biofeedback is effective for stress reduction and the regulation of consciousness.

First and foremost, stress in this context is defined as the activation of the sympathetic nervous system and the corresponding withdrawal of the parasympathetic branch. These physiological shifts directly affect heart activity. The heart rate variability provides a much more detailed overview over the heart activity. Consequently, for system that is supposed to reduce stress and improve consciousness the heart rate variability should be primarly tracked \cite{mcewen2017neurobiology} \cite{shaffer2017overview}.

This can be achieved by utilizing an rPPG approach, which is implemented by monitoring the green color channel of the video signal \cite{verkruysse2008remote}. The primary regions of interest are the cheeks, as this area is typically not covered by clothing or hair \cite{lempe2013roi}. To track this region, several methodologies exist, ranging from the classic Viola-Jones algorithm to landmark-based tracking approaches \cite{li2014remote} \cite{poh2010non}. Modern systems, however, employ artificial intelligence networks that utilize face meshes to track the region of interest. These frameworks are highly optimized and remain very fast even when used on mobile devices and should be primarly used \cite{kartynnik2019real}.

For real-time feedback, it is crucial that the underlying algorithms are computationally efficient. Furthermore, the system must remain robust against motion artifacts. In daily life, users do not remain perfectly still for extended periods. Therefore, the CHROM algorithm is ideally suited for this use case. It is fast to calculate as it leverages the standardized optical properties of human skin, and it has been proven to be resilient against motion changes \cite{dehaan2013chrom}. In contrast, other methods such as blind source separation techniques often require longer observation windows for an initial measurement or demand significant hardware resources. They also tend to fail under motion or in high-noise environments. Moreover, BSS sometimes struggle to identify the right color channel which might lead to pential errors \cite{poh2010non}. As highlighted by Debnath (2025), modern deep learning architectures are frequently very resource-intensive, requiring researches to develop specialized models for 'resource-constrained environments' \cite{Debnath25}. Compared to these complex neural networks, the CHROM algorithm is significantly simpler to implement and requires far less computational power \cite{dehaan2013chrom}. This efficiency ensures that the heart rate can be estimated immediately on standard hardware, which is essential for providing synchronized results without processing delays. Additionally, these networks are often trained on datasets that lack a sufficient variety of skin tones. This leads to the conclusion that a CHROM-based approach is best suited for this application \cite{Debnath25}.

In the next step, this physiological data must be converted into musical biofeedback. There are mixed opinions regarding the independent effects of music listening on stress reduction. While some papers argue that listening to music exerts a meditative effect and thereby decreases stress \cite{bernardi2006cardiovascular}, other studies suggest that the user must have the explicit intention to reduce their own stress levels \cite{linnemann2015music}. In addition, several studies utilized physical devices to track the physiological properties of the human body. Users have reported that these wearable sensors made them feel uncomfortable, which potentially introduced noise into the collected data \cite{pelletier2004effect}. A continuous mapping process is necessary to provide the user with immediate feedback regarding their own body \cite{dubus2013systematic}.

To achieve this, the system follows a sonification strategy based on parameter mapping to ensure a conscious transmission of information \cite{dubus2013systematic}. In this process, specific auditory dimensions have to be chosen carefully. According to Dubus and Bresin (2013), this should follow the principle of 'ecological perception'. When the stress or the heart beat is low (calm), the sound has to reflect this behavior. This shows that the choice of sonic material is decisive. It is important to verify the chosen strategy scientifically \cite{dubus2013systematic}.

The "Unwind" system is a practical example of these principles, as it successfully utilized nature sounds, such as wind noises, to imitate breathing patterns. Furthermore, this organic soundscape can be used to reflect the participant's arousal level \cite{yu2018unwind}. This follows the principle of "ecological perception" as mentioned before. If the body is calm, the soundscape has to reflect this calmness \cite{dubus2013systematic}.

Additionally, case studies involving the "Muse" headband have demonstrated that biofeedback can effectively increase conscious awareness and mitigate anxious thoughts. Biofeedback serves as an "anchor," preventing the user from ruminating on distracting or stressful thoughts \cite{app7121280}. This process also enables various health-promoting mechanisms through biofeedback-driven regeneration. The respiratory and cardiovascular systems are synchronized, and when this resonance frequency is reached, the body functions at its optimum. This stimulates the vagus nerve, making it possible to further lower stress levels and promote long-term recovery \cite{lehrer2014heart}.

\section{Future Outlook}

The rPPG technology is promising for the future, as it can track the heartbeat from a distance and even predict the heart rate under significant motion. Especially in an office environment, this technology could be employed to monitor the stress levels of employees. Together with musical feedback, it could be used daily to detect and decrease high levels of stress. The tracking does not have to be successful at all times. Detecting an increase in stress even once is enough to signal to the user that they are experiencing a high stress level.

The research on smaller artificial intelligence models that could be deployed on a personal computer is ongoing and could become realistic in the near future. It is also possible to combine this with other physiological measurements, such as breathing patterns or facial cues. Additionally, these systems are very cost-effective and can run on a simple digital camera or webcam.

On the other hand, there could be significant privacy issues, as users could be easily monitored with this technology. Therefore, it is important that strict privacy rules are established. Additionally, the software should run on the local computer to mitigate the risks of storing sensitive data in the cloud.





